hbm_paper_results

### 2024-01-04 paper_results.Rmd
plots, easier pulls

```{r}
sex.bias.t.tests(subj_sum.df)
```

>>>>

```{r}
sex.bias.t.tests(subj_sum.df)
sex.bias.t.tests(subj_sum.df, to_test="mean_cent_diff")
```

### Extremeness-Biases

Group at 0-0.25, >0.25 - .75 <, 0.75-1

```{r}
subj_sum.df <- subj_sum.df %>%
  mutate(cent_cat = as.factor(case_when(mean_centile <= 0.25 ~ "low",
                              mean_centile > 0.25 & mean_centile < 0.75 ~ "mid",
                              mean_centile >= 0.75 ~ "high")),
         z_cat = as.factor(case_when(mean_z <= -1 ~ "low",
                              mean_z > -1 & mean_z < 1 ~ "mid",
                              mean_z >= 1 ~ "high")))
```

```{r}
subj_sum.df %>%
  dplyr::filter(dataset == "cf.gamlss" | dataset == "cf.gam" | dataset == "cf.lm") %>%
  ggplot(aes(x=mean_z, y=mean_z_diff, color=sex)) +
  geom_point(alpha=0.5) +
  geom_smooth() +
  facet_wrap(~dataset, scales="free_y")
```
